Nail: A practical interface generator for data formats

### 2014-05-01 paper/osdi14/intro.tex
placeholders for citations in intro

Third, many data formats contain redundancies, such as repeating information in multiple structures.
Applications usually do not explicitly check for consistency, and if different applications use
different instances of the same value, an attacker can craft input that causes inconsistencies.
Furthermore, security vulnerabilities can occur when an application assumes two repetitions of the
same data to be consistent, such as allocating a buffer based on the value of one size field and copying into
that buffer based on the value of another.

>>>>

Third, many data formats contain redundancies, such as repeating information in multiple structures.
Applications usually do not explicitly check for consistency, and if different applications use
different instances of the same value, an attacker can craft input that causes inconsistencies~\cite{cve-python-zip-maybe}.
Furthermore, security vulnerabilities can occur when an application assumes two repetitions of the
same data to be consistent, such as allocating a buffer based on the value of one size field and copying into
that buffer based on the value of another~\cite{cve-some-example}.
